The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-07-30 manuscript.Rmd
update variable names

We investigated the proportion of species discovered since the publication of the faunistic lists using iDigBio records. They represent `r sum(recently_collected$gom_in_idig$min_year > 2001)` species for the Gulf of Mexico, and `r sum(recently_collected$pnw_in_idig$min_year > 1996)` species for the Pacific Northwest. While errors in geographic coordinates cannot be completely ruled out, it is more likely that the main contributing factor was that the authors of these checklists were not aware of the presence of these species based only on museum records, as these lists were mostly assembled from publications, and only a small fraction of museum records are used in publications. However, museum specimens are critical to validate the occurrence of species [@Rocha2014], especially for marine invertebrates for which species limits based on morphology have been known to be challenged by other lines of evidence including molecular data [@Knowlton2000].

>>>>

We investigated the proportion of species discovered since the publication of the faunistic lists using iDigBio and OBIS records. They represent `r sum(recently_collected$gom_in_dbs$min_year > 2001)` species for the Gulf of Mexico, and `r sum(recently_collected$pnw_in_dbs$min_year > 1996)` species for the Pacific Northwest. While errors in geographic coordinates cannot be completely ruled out, it is more likely that the main contributing factor was that the authors of these checklists were not aware of the presence of these species based only on museum records, as these lists were mostly assembled from publications, and only a small fraction of museum records are used in publications. However, museum specimens are critical to validate the occurrence of species [@Rocha2014], especially for marine invertebrates for which species limits based on morphology have been known to be challenged by other lines of evidence including molecular data [@Knowlton2000].
